Second-Generation Web Interface to Correcting ASR Output

### 2018-05-21 2018-ftc-vancouver/webapp.tex
zmínka o ostatních komunitních korpusových projektech (FTC2018)

\begin{filecontents}{citace.bib}
@inproceedings{kruuza2012making,
  title={Making Community and ASR Join Forces in Web Environment},
  author={Kr\r{u}za, Old{\v{r}}ich and Peterek, Nino},
  booktitle={International Conference on Text, Speech and Dialogue},
  pages={415--421},
  year={2012},
  organization={Springer}
}
@article{codd1970relational,
  title={A relational model of data for large shared data banks},
  author={Codd, Edgar F},
  journal={Communications of the ACM},
  volume={13},
  number={6},
  pages={377--387},
  year={1970},
  publisher={ACM}
}
@article{adenot2013web,
  title={Web audio api},
  author={Adenot, Paul and Wilson, Chris and Rogers, Chris},
  journal={W3C, October},
  volume={10},
  year={2013}
}
@article{abramov2015redux,
  title={Redux},
  author={Abramov, D},
  journal={React Community, c},
  year={2015}
}
@article{hajek2007cesky,
  title={\v{C}esk\'{y} mystik Karel Mako\v{n}},
  author={Jurik H\'{a}jek},
  journal={Dingir},
  year={2007},
  volume={2007/4},
  pages={142--143},
  publisher={Dingir, s.r.o.},
  ISSN={1212-1371},
  editor={Zden\v{e}k Vojt\'{i}\v{s}ek}
}
\end{filecontents}

@@

% wreally: pause interval
%          auto loop
%          templates
%          pedál
%          Fka
%          bez alignmentu

@@

>>>>

\begin{filecontents}{citace.bib}
@inproceedings{kruuza2012making,
  title={Making Community and ASR Join Forces in Web Environment},
  author={Kr\r{u}za, Old{\v{r}}ich and Peterek, Nino},
  booktitle={International Conference on Text, Speech and Dialogue},
  pages={415--421},
  year={2012},
  organization={Springer}
}
@article{codd1970relational,
  title={A relational model of data for large shared data banks},
  author={Codd, Edgar F},
  journal={Communications of the ACM},
  volume={13},
  number={6},
  pages={377--387},
  year={1970},
  publisher={ACM}
}
@article{adenot2013web,
  title={Web audio api},
  author={Adenot, Paul and Wilson, Chris and Rogers, Chris},
  journal={W3C, October},
  volume={10},
  year={2013}
}
@article{abramov2015redux,
  title={Redux},
  author={Abramov, D},
  journal={React Community, c},
  year={2015}
}
@article{hajek2007cesky,
  title={\v{C}esk\'{y} mystik Karel Mako\v{n}},
  author={Jurik H\'{a}jek},
  journal={Dingir},
  year={2007},
  volume={2007/4},
  pages={142--143},
  publisher={Dingir, s.r.o.},
  ISSN={1212-1371},
  editor={Zden\v{e}k Vojt\'{i}\v{s}ek}
}
@inproceedings{ide2010manually,
  title={The manually annotated sub-corpus: A community resource for and by the people},
  author={Ide, Nancy and Fellbaum, Christiane and Baker, Collin and Passonneau, Rebecca},
  booktitle={Proceedings of the ACL 2010 conference short papers},
  pages={68--73},
  year={2010},
  organization={Association for Computational Linguistics}
}
@article{bojar2008czeng,
  title={CzEng 0.7: Parallel Corpus with Community-Supplied Translations},
  author={Bojar, Ond{\v{r}}ej and Jan{\'\i}{\v{c}}ek, Miroslav and {\v{C}}e{\v{s}}ka, Pavel and Be{\v{n}}a, Peter and others},
  journal={LREC 2008},
  year={2008}
}
@inproceedings{5494979,
  author={M. Marge and S. Banerjee and A. I. Rudnicky},
  booktitle={2010 IEEE International Conference on Acoustics, Speech and Signal Processing},
  title={Using the Amazon Mechanical Turk for transcription of spoken language},
  year={2010},
  volume={},
  number={},
  pages={5270-5273},
  keywords={linguistics;natural language processing;speech processing;Amazon mechanical turk service;MTurk marketplace;Rover voting scheme;speaker demographics;spoken language transcription;transcription guideline;Computer science;Costs;Demography;Gold;Guidelines;Humans;Natural languages;Recruitment;Speech synthesis;Streaming media;crowd sourcing;speech transcription},
  doi={10.1109/ICASSP.2010.5494979},
  ISSN={1520-6149},
  month={March},
}
@article{reese2010wikicorpus,
  title={Wikicorpus: A word-sense disambiguated multilingual wikipedia corpus},
  author={Reese, Samuel and Boleda, Gemma and Cuadros, Montse and Rigau, German},
  year={2010},
  publisher={Citeseer}
}
\end{filecontents}

@@

@@

\subsection{Corpora}

Our project is not the first community-driven corpus annotation. We can mention
the Manually annotated sub-corpus\cite{ide2010manually}, where annotations of
various kinds are gathered from volunteers, or the
Wikicorpus\cite{reese2010wikicorpus}, a corpus of Wikipedia articles with some
linguistic annotation. Our project may reach profound similarities with these in
the future, when we no longer focus on the transcription itself but rather on
annotation. There is also CzEng\cite{bojar2008czeng}, the Czech-English Parallel
Corpus, where a large part of the translation is provided by volunteers. The
similarity in setting is considerable as both projects involve a
machine-produced erroneous derivative of the original material (in our case
audio transcriptions, in the case of CzEng Czech translations of English texts),
and a community of volunteers corrects these. But the specifics of the projects
bring different challenges and dictate different approaches. Finally, Marge
2009\cite{5494979} investigates using The Mechanical Turk to obtain audio
transcriptions.
